Exploring the Pareto front of multi-objective COVID-19 mitigation policies using reinforcement learning

### 2023-03-24 paper/main.tex
pieter comments

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Analysing COVID-19 deconfinement policies}
\label{sec:experiments}
Our goal is to use PCN to learn deconfinment strategies in the \momdpname\ environment. We aim to learn policies that balance between the epidemiological objective of minimising the attack rate and the social burden experienced by the population. To this end we consider two cases for the vectorial reward functions $[\mdprewardfn_\text{ARH}, \mdprewardfn_\text{SB}]$ and $[\mdprewardfn_\text{ARI}, \mdprewardfn_\text{SB}]$, to learn and analyse policies under different targets with respect to the considered attack rate.

To conduct this analysis, we evaluate our extension of PCN for continuous action-spaces on both the Binomial model. \todo{reason for binomial}. As explained in Section~\ref{sec:pcn-stochastic}, we extend PCN for environments with stochastic transitions. While all results in this Section concern the Binomial model, we observe similar performance on the ODE model, showing that our extension does resolve the stochasticity issue. These results are available in the SI.

Conform to \citet{abrams2021modelling}, the simulation starts on the 1st of March 2020, by seeding a number of infections in the population. Two weeks later, on the 14th of March, the Belgian government initiated a full lockdown of the country. This is implemented by fixing the actions $p_w, p_s, p_l$ to $0.2, 0, 0.1$ respectively. This lockdown ended on the 4th of May 2020, at which point the government decided on a multi-phase exit strategy to incrementally reduce teleworking, reopen schools and allow leisure activities, such as the re-opening of bars and the cultural sector. It is from this day onward that PCN aims to learn policies for diverse exit strategies, compromising between the total number of daily new hospitalizations and the total number of contacts lost as a proxy for social burden. The simulation lasts throughout the school holidays (from 01/07/2020 to 31/08/2020). Schools are closed during the school holidays, which is simulated by setting $p_s = 0$, regardless of the corresponding value outputted by the policy, i.e., during periods of school closure $p_s$ is ignored.

@@

To evaluate the quality of the policies discovered by PCN, we compare it to a baseline. The baseline consists of a set of 100 fixed policies, that iterate over all the possible social restriction levels, with values ranging from 0 to 1. Concretely, each policy uses a fixed proportional reduction $p_w=p_l=p_s=u, u\sim\mathcal{U}(0, 1)$ throughout the episode. In other words, the fixed policies directly operate in a fine-grained manner on the whole contact reduction function $\hat{C}$. This allows us to obtain a strong baseline for potential exit strategies over the objective space. We note that while such fixed policies are a feasible approach, they do not scale well in terms of action and objective spaces and they will not be able to provide an adaptive restriction level, which is what we aim to provide using PCN.

@@

\begin{figure}
    \centering
    \input{fig/arh_binomial_both}
    \caption{The Pareto front of policies discovered by PCN using the Binomial model, showing the different compromises between the number of hospitalizations and the number of lost contacts. As the budget increases, so does the coverage set learnt by PCN. Changes are most noticeable in the less restrictive trade-offs in terms of social burden.}
    \label{fig:pf-binomal-arh-budgets}
\end{figure}

@@

We learn a coverage set that ranges from imposing minimal restrictions to enforcing many restrictions (see Figure~\ref{fig:policy-execution}). The coverage set is shown in Figure~\ref{fig:pf-binomal-arh-budgets}. On the right, we display the coverage set of the best-performing run in terms of hypervolume, for each budget setting. On the left, we show an interpolated average of the coverage sets learned by the different runs.

Regardless of the imposed budget, we notice that the coverage sets discovered by PCN almost completely dominate the coverage set of the baseline, demonstrating that there are better alternatives to the fixed policies. This is most visible in the compromising policies, where one has to carefully choose when to remove social restrictions while at the same time minimizing the impact on daily new hospitalizations. In these scenarios, PCN discovers policies that can drastically reduce the total number of new hospitalizations (e.g. more than $20000$) for the same social burden. Analysing the executions of such policies (see Figure~\ref{fig:policy-execution}, middle plot) shows a flattened hospitalization curve, with a gradual increase of social freedom during the school holidays such that the peak stays stable and gradually decreases over time.

@@

@@

\begin{figure}
    \centering
    \input{fig/budget_5}
    \caption{Selection of policies learned by $\text{PCN}_{b=5}$, from most restrictive in terms of social burden (top) to least restrictive (bottom).
    }
    \label{fig:policy-execution}
\end{figure}

Looking at the coverage sets displayed in Figure~\ref{fig:pf-binomal-arh-budgets}, we notice that the budget impacts the coverage set that has been learnt. In general, an increase of budget results in an increasingly better coverage set. This is to be expected, as a higher budget give the agent more freedom to change its actions as the epidemic progresses. However, we also notice that this increase of coverage sets is not necessarily gradual. Between the run with a budget of 2 and budget of 3, the difference in coverage set seems marginal. \todo{insight}.

Moreover, we observe that the improvement concentrates around the less restrictive policies in terms of social burden. We believe that this regio contains the most complex policies, as these try to maintain as much social freedom as possible, while containing the number of hospitalisations. We believe that, in these cases, the timing of the actions greatly correlate with the timing and duration of the peak of the epidemic, and a higher budget allows for more fine-grained control about managing this timing. To confirm this, we select, for each budget setting, the solution where the difference in performance is most noticeable, corresponding to the solutions with a total number of hospitalisations around $80000$. We plot the execution of the corresponding policies in Figure~\ref{fig:pe-binomial-arh-budgets} and analyse the difference they make in terms of social burden. First, we notice that the lower-budget policies are unable to lessen the social restrictions past the peak of the epidemic. In contrast, the setting with no budget restrictions finely controls the restrictions as the epidemic progresses, completely removing restrictions by the end of the wave. We note how the policy with a budget of 5 ressembles the execution of the one without restrictions but that, due to its budget, is unable to progressively lessen the restrictions and instead resorts to a halfway compromise. \todo{corresponding SB numbers}

Compared to this specific regio of the coverage set, the difference in performance between different budget settings seems marginal around the extremas. \todo{explain}

Finally, we observe that, while the extremas deliver similar trade-offs regardless of the chosen budget, the results differ for the setting without budget restrictions. Indeed, in this setting, PCN does not seem to learn the most and least restrictive policies, even though there are no constraints on the action-set. As explained in Section~\ref{sec:pcn-policy-exploration}, PCN searches for increasingly better solutions using a stochastic policy. Thus, at every timestep, the action can change compared to the previous one. Continuously outputting the same action (e.g., no social restrictions) becomes a complicated task. In comparison, for the settings with a limited budget, the action stays the same as the previous one once the budget has been spent. It is thus easier to discover the most extreme policies. Thus, in the specific case where we impose no budget, we believe the freedom of action actually hinders PCN's search.

\begin{figure}
    \centering
    \input{fig/all_budgets}
    \caption{Execution of the policies attaining a number of hospitalisations around $80000$, for different budgets. From top to bottom are displayed the policy executions of runs with budget 2,3,4,5 and no-limit, respectively. We notice that the lower-budget policies are unable to lessen the social restrictions past the peak. The setting with no budget restrictions finely controls the restrictions as the epidemic progresses, completely removing restrictions by the end of the wave. Finally, there is no consensus on which social environment to restrict most, some policies providing similar restrictions for $p_w$ and $p_l$, while others putting harsher restrictions on one social environment than the other.
    }
    \label{fig:pe-binomial-arh-budgets}
\end{figure}

@@

We now assess the difference in coverage sets when optimizing on $\mdprewardfn_\text{ARH}$ versus $\mdprewardfn_\text{ARI}$. Although these reward functions have a different scale (there are more infected persons than hospitalised ones), our experiments show that infections and hospitalizations are correlated. This is expected, as during the initial phase of the epidemic, limited immunity was present in the population (few natural immunity and no vaccines), which induces a tight coupling between infection and hospitalisation cases. This is confirmed in Table~\ref{tab:coverage-set}. In this table, we show the different performance metrics (hypervolume, $I_\varepsilon$, $I_{\varepsilon-mean}$) with respect to the objectives $[\mdprewardfn_\text{ARH}, \mdprewardfn_\text{SB}]$. However, the left-side of the table shows the experiments where these objectives are also used as optimization criterions, while the right-side shows the experiments using $[\mdprewardfn_\text{ARI}, \mdprewardfn_\text{SB}]$ as optimization criterions.

Even with the $\mdprewardfn_\text{ARI}$, the increased budget shows an increase in hypervolume in terms of hospitalisations. Moreover, those hypervolumes are close to the ones trained on $\mdprewardfn_\text{ARH}$, inidicating that their coverage sets are similar. However, regardless of the imposed budget, the hypervolumes are slightly worse. This is to be expected, since those experiments are not directly optimising on $\mdprewardfn_\text{ARH}$. We make similar conclusions for $I_\varepsilon$. For budgets 2, 3 and 5, the difference between the worst-performing policy for the $\mdprewardfn_\text{ARI}$ variant and the $\mdprewardfn_\text{ARH}$ is less than $0.01$, indicating less than $1\%$ difference in return values between the two variants when comparing their worst-performing policy. As an exception, we notice that PCN without budget restrictions results in better performance across every metric for the $\mdprewardfn_\text{ARI}$ variant. Still, due to the high standard deviation of the no-budget, $\mdprewardfn_\text{ARH}$ setting, we do not believe this difference is meaningfull. \todo{some kind of meaningful conclusion}

@@

The dataset of trajectories that PCN is trained on is pruned over time to keep only the most relevant trajectories. The returns of these trajectories are used in Figure~\ref{fig:pf-binomal-arh-budgets} to show the discovered coverage set. Each of these returns can be used as desired return for policy execution. We now assess the robustness of the executed policies, by comparing the return obtained after executing the policy with the corresponding target return. For each run, we execute the policy $10$ times and compute the $I_\varepsilon$ and $I_{\varepsilon-mean}$ metrics with respect to the coverage set learned during the run. We show that the executed policies reliably obtain returns that are similar to the desired return used to condition PCN.

Results are shown in Table~\ref{tab:pcn-robustness}. The $I_\varepsilon$ indicators shows that, regardless of the budget, the decision maker will lose at worst a $0.050$ normalized return in any of the objectives. On average, it will lose $0.010$ normalized returns. Moreover, we emphasize that the learned coverage set contains the non-dominated returns across the whole training procedure. Since the Binomial model is stochasticity, for multiple executions of the same policy, the executions that remains in the coverage set is the one with advantageous transitions due to this stochasticity. Thus, we expect our policy-executions to obtain slightly worse results than the target-solution selected from the coverage set. In light of this, we conclude that the policies trained by PCN are reliable and produce returns as close as possible from their chosen target.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related work}
Reinforcement learning (RL) has been used in conjunction with epidemiological models to learn policies to limit the spread of diseases and predict the effects of possible mitigation strategies \cite{probert2019context,ernst2006clinical}. For example, RL has been used extensively in modelling and controlling the spread of influenza \cite{das2008large,libin2020,libin2018bayesian}.

@@

Multi-objective methods have also been deployed to learn optimal strategies to mitigate the spread of COVID-19. Wan et al. \cite{wan2021multi} implement a model-based multi-objective policy search method and demonstrate their method on COVID-19 data from China. Given the method is model-based, a model of the transition function must be learned by sampling from the environment. The method proposed by Wan et al. \cite{wan2021multi} only considers a discrete action space which limits the application of their algorithm. Wan et al. \cite{wan2021multi} use linear weights to compute a set of Pareto optimal policies. However, methods which use linear weights can only learn policies on the convex-hull of the Pareto front \cite{vamplew2008limitations}, therefore the full Pareto front cannot be learned. It is important to note the method proposed by Kompella et al. \cite{kompella2020reinforcement} considers multiple objectives. However, the objectives are combined using a weighted sum with hand-tuned weights which are determined by the authors. The weighted sum is applied by the reward function and a single objective RL method is used to learn a single optimal policy.
In contrast to previous work, our approach makes no assumptions regarding the scalarisation function of the user and is able to discover Pareto fronts of arbitrary shape.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and discussion}
Making decisions on how to mitigate epidemics has important ethical implications with respect to public health and societal burden. In this regard, it is crucial to approach this decision making from a balanced perspective, to which end we argue that multi-objective decision making is crucial. In this work, we establish a novel approach, i.e., an expert system, to study multi-faceted policies, and this approach shows great potential with respect to future epidemic control. We are aware of the ethical implications that expert systems have on the decision process and we make the disclaimer that all results based on, or derived from, the expert system that we propose should be carefully interpreted by experts in the field of public health, and in a much broader context of economics, well-being and education. We note that the work in this manuscript was conducted by a multi-disciplinary consortium that includes computer scientists and scientists with a background public health, epidemiology and bio-statistics.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Analysing COVID-19 deconfinement policies}
\label{sec:experiments}
Our goal is to use PCN to learn deconfinment strategies in the \momdpname\ environment. We aim to learn policies that balance between the epidemiological objective of minimising the attack rate (i.e., $\mdprewardfn_\text{ARH}$ for hospitalisation and $\mdprewardfn_\text{ARI}$ for infection) and the social burden (i.e., $\mdprewardfn_\text{SB}$) experienced by the population population due to the implement mitigation measures. To this end, we consider two cases for the vectorial reward functions $[\mdprewardfn_\text{ARH}, \mdprewardfn_\text{SB}]$ and $[\mdprewardfn_\text{ARI}, \mdprewardfn_\text{SB}]$, to learn and analyse policies under different targets with respect to the considered attack rate.

To conduct this analysis, we apply our extension of PCN for continuous action-spaces on the \momdpname\ model. As explained in Section~\ref{sec:pcn-stochastic}, we extend PCN for environments with stochastic transitions.

Conform to \citet{abrams2021modelling}, the simulation starts on the 1st of March 2020, by seeding a number of infections in the population. Two weeks later, on the 14th of March, the Belgian government initiated a full lockdown. This is implemented by fixing the actions $p_w, p_s, p_l$ to $0.2, 0, 0.1$ respectively. This lockdown ended on the 4th of May 2020, at which point the government decided on a multi-phase exit strategy to incrementally reduce teleworking, reopen schools and allow leisure activities, such as the re-opening of bars and the cultural sector. It is from this day onward that PCN aims to learn policies for diverse exit strategies, compromising between the total number of daily hospitalizations and the total number of contacts lost as a proxy for social burden. The simulation lasts throughout the school holidays (from 01/07/2020 to 31/08/2020). Schools are closed during the school holidays, which is simulated by setting $p_s = 0$, regardless of the corresponding value outputted by the policy, i.e., during periods of school closure $p_s$ is ignored.

@@

To evaluate the quality of the policies learned by PCN, we compare PCN to a baseline. This baseline consists of a set of 100 fixed policies, that iterate over all the possible social restriction levels, with values ranging between 0 and 1. Concretely, each policy uses a fixed proportional reduction $p_w=p_l=p_s=u, u\sim\mathcal{U}(0, 1)$ throughout the episode. In other words, the fixed policies directly operate in a fine-grained manner on the whole contact reduction function $\hat{C}$. This allows us to obtain a strong baseline for potential exit strategies over the objective space. We note that while such fixed policies are a feasible approach, they do not scale well in terms of action and objective spaces and they will not be able to provide an adaptive restriction level, which is what we aim to provide using PCN.

@@

\begin{figure}
    \centering
    \input{fig/arh_binomial_both}
    \caption{The Pareto front of policies discovered by PCN using \momdpname, showing the different compromises between the number of hospitalizations and the number of lost contacts. On the right, we show, for each budget setting (colored, subscript indicates budget) the coverage set learned by the best performing run. On the left, we show an interpolated average of the coverage sets learned by the different runs, with the shaded regions corresponding to the standard deviation. For comparison, the basline is displayed on both plots (in black). As the budget increases, so does the size of the coverage set learnt by PCN. Changes are most noticeable in the less restrictive trade-offs in terms of social burden.}
    \label{fig:pf-binomal-arh-budgets}
\end{figure}

@@

We learn a coverage set (see Figure~\ref{fig:pf-binomal-arh-budgets}) that ranges from imposing minimal restrictions to enforcing many restrictions. In Figure~\ref{fig:pf-binomal-arh-budgets}, we display on the right the coverage set of the best-performing run in terms of hypervolume, for each budget setting. On the left, we show an interpolated average of the coverage sets learned by the different runs.

Regardless of the imposed budget, we notice that the coverage sets discovered by PCN almost completely dominate the coverage set of the baseline, demonstrating that there are better alternatives to the fixed policies. This is most evident in the compromising policies, where one has to carefully choose when to remove social restrictions while at the same time minimizing the impact on daily new hospitalizations. In these scenarios, PCN learns policies that drastically reduce the total number of new hospitalizations (e.g., more than $20000$) for the same social burden. We analyse the executions of such policies in Figure~\ref{fig:policy-execution} (middle plot), that shows a flattened hospitalization curve, with a gradual increase of social freedom during the school holidays such that the curve of the epidemic is flattened and gradually decreases over time.

@@

Finally, the top plot shows that, without imposing social restrictions, the number of hospitalisations peaks on the 15th of June. By the beginning of July, the epidemic has spread out over the majority of the population \todo{herd immunity?}, and the number of admissions at the hospital has been reduced to a fraction of the number of hospitalisations at the peak. Thus, without social restrictions, we do not take advantage of the natural decrease of social contacts due to school holidays, as the majority of the population has already been infected before the start of the holidays. \todo{mention the slow decrease of $p_l$ during the summer? This is simply due to PCN not having found better}

@@

\begin{figure}
    \centering
    \input{fig/budget_5}
    \caption{Selection of policies learned by $\text{PCN}_{b=5}$, from most restrictive in terms of social burden (top) to least restrictive (bottom). The x-axis represents the time, starting from the end of the lockdown, on the 4th of May, until the end of the school holidays, on the 1st of September. Since the lockdown is simulated before the start of the exit strategy, the start-state differs for each episode (i.e., the hospital already contains infected individuals). The left y-axis represents the number of individuals affected by the epidemic. The full-lined plots represent the number of individuals admitted into the hospital, ICU and deceased between the last timestep and the current one. The plot showing the newly deceased individuals closely relates to the ICU admissions. The right y-axis represents the proportional reduction in effect, with 1 meaning a business-as-usual policy, and 0 meaning a complete suppression of social contacts. The dotted-lined plots represent the proportional reductions for the work, leasure and school environments. We note that the school reduction automatically goes to 0 at the start of the school holidays.
    }
    \label{fig:policy-execution}
\end{figure}

Figure~\ref{fig:pf-binomal-arh-budgets} demonstrates that the budget impacts the learnt coverage set. In general, an increase of budget is associated with an increasingly better coverage set, as policies learned using a higher budget dominate the ones learned with a lower budget. This is to be expected, as a higher budget give the agent more freedom to change its actions as the epidemic progresses. However, we also notice that this increase of coverage sets is not necessarily gradual. Between the run with a budget of 2 and budget of 3, the difference in coverage set seems marginal. \todo{insight}.

Moreover, we observe that the difference is concentrated around the less restrictive policies in terms of social burden. We hypothesise that this region contains the most complex policies, as these try to maintain as much social freedom as possible, while containing the number of hospitalisations. In these cases, the timing of the actions greatly correlate with the timing and duration of the peak of the epidemic, and a higher budget allows for more fine-grained control about managing this timing. To confirm this, we select, for each budget setting, the solution where the difference in performance is most noticeable, corresponding to the solutions with a total number of hospitalisations around $80000$. We plot the execution of the corresponding policies in Figure~\ref{fig:pe-binomial-arh-budgets} and analyse their impact in terms of social burden. First, we observe that the lower-budget policies are unable to reduce the social restrictions past the peak of the epidemic. In contrast, the setting with no budget restrictions finely controls the restrictions as the epidemic progresses, completely removing restrictions by the end of the wave. Second, we note that the policy with a budget of 5 ressembles the execution of the one without restrictions. However, due to its budget, the policy is unable to progressively reduce the restrictions and instead resorts to a halfway compromise. \todo{corresponding SB numbers.} Compared to this specific region of the coverage set, the difference in performance between different budget settings seems marginal around the extremas. At the extremas, the policies are less complex (e.g., business-as-usual, resulting in the same action executed throughout the episode) and are thus less impacted by the budget restrictions.

Finally, we observe that, while the extremas deliver similar trade-offs for any of the chosen budgets, these trade-offs differ for the setting without budget restrictions. Indeed, in this setting, PCN does not learn the most extreme policies with respect to restrictions, even though there are no constraints on the action-set. As explained in Section~\ref{sec:pcn-policy-exploration}, PCN searches for increasingly better solutions using a stochastic policy. Thus, at every timestep, the action can change compared to the previous one. Continuously outputting the same action (e.g., no social restrictions) becomes a complicated task. In comparison, for the settings with a limited budget, the action stays the same as the previous one once the budget has been spent. As such, it is easier to learn the most extreme policies. Thus, in the specific case where we impose no budget, the freedom of action actually hinders PCN's search, for certain regions of the rweard-space.

\begin{figure}
    \centering
    \input{fig/all_budgets}
    \caption{Execution of the policies attaining a number of hospitalisations around $80000$, for different budgets. From top to bottom we display the policy executions with budget 2,3,4,5 and no-limit, respectively. We notice that the lower-budget policies are unable to reduce the social restrictions past the peak. The setting without budget restrictions finely controls the restrictions as the epidemic progresses, completely removing restrictions by the end of the wave. Finally, there is no consensus on which social environment to restrict most: certain policies provide similar restrictions for $p_w$ and $p_l$, while others impose harsher restrictions on one social environment than the other.
    }
    \label{fig:pe-binomial-arh-budgets}
\end{figure}

@@

Next, we assess the difference in coverage sets when optimizing on $\mdprewardfn_\text{ARH}$ versus $\mdprewardfn_\text{ARI}$. Although these reward functions have a different scale (there are more infected persons than hospitalised ones), our experiments show that infections and hospitalizations are correlated. This is expected, as during the initial phase of the epidemic, limited immunity was present in the population (i.e., limited natural immunity and no vaccines), which induces a tight coupling between infection and hospitalisation cases. This is confirmed in Table~\ref{tab:coverage-set}. In this table, we show the different performance metrics (hypervolume, $I_\varepsilon$, $I_{\varepsilon-mean}$) with respect to the objectives $[\mdprewardfn_\text{ARH}, \mdprewardfn_\text{SB}]$. The table is split in two parts. The left-side shows the different performance metrics, for PCN using $[\mdprewardfn_\text{ARH}, \mdprewardfn_\text{SB}]$ as optimization criterions. The right-side shows the same performance metrics, but with PCN using $[\mdprewardfn_\text{ARI}, \mdprewardfn_\text{SB}]$ as optimization criterions.

Even with the $\mdprewardfn_\text{ARI}$, the increased budget shows an increase in hypervolume in terms of hospitalisations. Moreover, those hypervolumes are close to the ones trained on $\mdprewardfn_\text{ARH}$, indicating that their coverage sets are similar. However, regardless of the imposed budget, the hypervolumes are slightly worse. This is to be expected, since those experiments are not directly optimising on $\mdprewardfn_\text{ARH}$. We make similar conclusions for $I_\varepsilon$. For budgets 2, 3 and 5, the difference between the worst-performing policy for the $\mdprewardfn_\text{ARI}$ variant and the $\mdprewardfn_\text{ARH}$ is less than $0.01$, indicating less than $1\%$ difference in return values between the two variants when comparing their worst-performing policy. As an exception, we notice that PCN without budget restrictions results in better performance across every metric for the $\mdprewardfn_\text{ARI}$ variant. Still, due to the high standard deviation of the no-budget, $\mdprewardfn_\text{ARH}$ setting, we do not believe this difference is meaningfull. \todo{some kind of meaningful conclusion}

@@

The dataset of trajectories that PCN is trained on is pruned over time to keep only the most relevant trajectories. The returns of these trajectories are used in Figure~\ref{fig:pf-binomal-arh-budgets} to show the learned coverage set. Each of these returns can be used as desired return for policy execution. We now assess the robustness of the executed policies, by comparing the return obtained after executing the policy with the corresponding target return. For each run, we execute the policy $10$ times and compute the $I_\varepsilon$ and $I_{\varepsilon-mean}$ metrics with respect to the coverage set learned during the run. We show that the executed policies reliably obtain returns that are similar to the desired return used to condition PCN.

Results are shown in Table~\ref{tab:pcn-robustness}. The $I_\varepsilon$ indicators shows that, regardless of the budget, the decision maker will lose at worst a $0.050$ normalized return in any of the objectives. On average, it will lose $0.010$ normalized returns, i.e., on average, the return obtained by executing a policy will either result in an additional $1441$ hospitalisations than expected, or result in $12$ additional social contacts lost. Moreover, we emphasize that the learned coverage set contains the non-dominated returns encountered over the whole training procedure. Since the \momdpname\ model is stochastic, for multiple executions of the same policy, the executions kept in the coverage sets are the ones for which the samples from the binomial-chain resulted in a better progression of the epidemic than average. Thus, we expect our policy-executions to be close to the target selected from the coverage set, but not on exactly target. Based on this analysis, we conclude that the policies trained by PCN are robust and produce returns as close as possible from their chosen target.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related work}
Reinforcement learning (RL) has been used in conjunction with epidemiological models to learn policies to limit the spread of diseases and predict the effects of possible mitigation strategies \cite{probert2019context}. For example, RL has been used to model the mitigation of influenza \cite{das2008large,libin2020,libin2018bayesian}.

@@

Multi-objective methods have also been deployed to learn optimal strategies to mitigate the spread of COVID-19. Wan et al. \cite{wan2021multi} implement a model-based multi-objective policy search method and demonstrate their method on COVID-19 data from China. Given that this method is model-based, a model of the transition function must be learned by sampling from the environment. The method proposed by Wan et al. \cite{wan2021multi} only considers a discrete action space which limits the application of their algorithm. Wan et al. \cite{wan2021multi} use linear weights to compute a set of Pareto optimal policies. However, methods which use linear weights can only learn policies on the convex-hull of the Pareto front \cite{vamplew2008limitations}, therefore the full Pareto front cannot be learned. We note that the method proposed by Kompella et al. \cite{kompella2020reinforcement} considers multiple objectives. However, the objectives are combined using a weighted sum with hand-tuned weights which are determined by the authors. The weighted sum is applied by the reward function and a single objective RL method is used to learn a single optimal policy.
In contrast to previous work, our approach makes no assumptions regarding the scalarisation function of the user and is able to discover Pareto fronts of arbitrary shape.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and discussion}
Making decisions on how to mitigate epidemics has important ethical implications with respect to public health and societal burden. In this regard, it is crucial to approach this decision making from a balanced perspective, to which end we argue that multi-objective decision making is crucial. In this work, we establish a novel approach, i.e., an expert system, to study multi-faceted policies, and this approach shows great potential with respect to future epidemic control. We are aware of the ethical implications that expert systems have on the decision process and we make the disclaimer that all results based on, or derived from, the expert system that we propose should be carefully interpreted by experts in the field of public health, and in a much broader context of economics, well-being and education. We note that the work in this manuscript was conducted by a interdisciplinary consortium that includes computer scientists and scientists with a background public health, epidemiology and bio-statistics.
